
\documentclass{article}


\begin{document}
	
\section{File Structure}

\subsection{.inp}

Inp files contain the input values for westersim.

The first line contains a string for the name of the molecule.

The first section, after the molecule name, is Controls. This section sets global variables for westersim.

\begin{tabular}{c c c}
	NFOLD & integer & The fold value for the rotor \\
	S & float & Total spin value \\
	TK & float & Temperature in Kelvin \\
	RUNmode & flag & ESF for energy, simulation, and fit. Defines which westerfit programs will run. \\
	mcalc & integer & defines the size of the torsional basis \\
	vtmax & integer & maximum value of vt \\
	Jmax & float & maximum value of J \\
	vmin & float & minimum frequency value in GHz \\
	vmax & float & maximum frequency value in Ghz \\
\end{tabular}

The second section is the values of all the second order coefficients. It's in a pseudo-fixed-width format delimited by semicolons. The first column is the name of the coefficient. The second is its value in MHz (except F, V$_3$, and $\rho$, which are in wavenumbers, wavenumbers, and unitless, respectively). The third is currently an on/off flag that can be 0.0 or 1.0, but in the future should have scaling factors for fitting.

\begin{tabular}{c c}
	A & MHz \\
	B & MHz \\
	C & MHz \\
	Dab & MHz \\
	$\epsilon$zz & MHz \\
	$\epsilon$xx & MHz \\
	$\epsilon$zz & MHz \\
	$\epsilon$xz & MHz \\
	$\chi$zz & MHz \\
	$\chi$xmy & MHz \\
	$\chi$xz & MHz \\
	F & cm$^{-1}$ \\
	$\rho$ & dimensionless \\
	V$_n$ & cm$^{-1}$ \\
	$\eta$ & MHz \\
\end{tabular}

The third section is the operators. They are defined by a value, a scaling factor (again, currently functioning as an on/off flag), values a-h, and stg (stage).

A-h are the values to be substituted into the parameters listed above the operator section.

Stage is set to 0 for dipole operators and 1 for Hamiltonian operators. -n indicates that the parameter value is the product of the parameter value in that line and the line n lines above, and uses the same stage as the above line.


\subsection{.eng}
	
Eng files contain the energy listings produced by westersim.
	
	\begin{tabular}{c c c c c c c}
		1 & 2 & 3 & 4 & 5 & 6 & 7 \\
		J & N & K$_a$ & K$_c$ & m & $\sigma$ & E \\
	\end{tabular}
	
\subsection{.lne and .cat}

Lne files contain the line lists used by westerfit. Cat files contain the line lists produced by westersim.


	\begin{tabular}{c c c c c c c c c c c c}
		1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
		J$_u$ & N$_u$ & K$_{au}$ & K$_{cu}$ & m$_u$ & J$_l$ & N$_l$ & K$_{al}$ & K$_{cl}$ & m$_l$ & freq & unc \\
	\end{tabular}


	
\end{document}